\bf Visual Inference for Significance and Goodness-of-Fit Testing for a Social Network Model

### 2017-11-02 ASApaper/paper-child.Rnw
formatting changes

<<goftab, cache = TRUE, results='asis'>>=
turk22_gof <- read_csv("data/turk22-gof.csv")
turk22_gof_stats <- turk22_gof %>% group_by(pic_id) %>% 
  summarize(npickdata = sum(datapick), total = n(), 
          pvinf = map2_dbl(npickdata, total, pV, m = 6, scenario = 3))
turk22_gof_stats %>% separate(pic_id, into = c("discard", "model", "rep"), sep = c(2,3)) -> print_gof_stats
print_gof_stats %>% select(-discard) %>% mutate(model = paste0("M", (as.integer(model)-1)))-> print_gof_stats
names(print_gof_stats) <- c("Model", "Replicate", "Data Picks", "Total Viewers", "p-value")
print_gof_stats$`p-value` <- ifelse(print_gof_stats$`p-value` < .0001, "< 0.0001", as.character(round(print_gof_stats$`p-value`,4)))
print(xtable::xtable(print_gof_stats, label = "tab:gofstats", caption = "An overview of the results from our 12 goodness-of-fit lineup tests.", digits = 4), caption.placement = "bottom", include.rownames = FALSE)
@

>>>>

<<goftab, cache = TRUE, results='asis'>>=
turk22_gof <- read_csv("data/turk22-gof.csv")
turk22_gof_stats <- turk22_gof %>% group_by(pic_id) %>% 
  summarize(npickdata = sum(datapick), total = n(), 
          pvinf = map2_dbl(npickdata, total, pV, m = 6, scenario = 3))
turk22_gof_stats %>% separate(pic_id, into = c("discard", "model", "rep"), sep = c(2,3)) -> print_gof_stats
print_gof_stats %>% select(-discard) %>% mutate(model = paste0("M", (as.integer(model)-1)))-> print_gof_stats
names(print_gof_stats) <- c("Model", "Replicate", "Data Picks", "Total Viewers", "p-value")
print_gof_stats$Model[c(2:3,5:6,8:9,11:12)] <- ""
print_gof_stats$Model[2] <- "jtt party"
print_gof_stats$Model[5] <- "jtt sex"
print_gof_stats$Model[8] <- "stt party"
print_gof_stats$`p-value` <- ifelse(print_gof_stats$`p-value` < .0001, "< 0.0001", sprintf("%.4f", print_gof_stats$`p-value`))
print(xtable::xtable(print_gof_stats, label = "tab:gofstats", caption = "An overview of the results from the 12 goodness-of-fit lineup tests.", digits = 4,
                      align="rlrrrr"), caption.placement = "bottom", include.rownames = FALSE, hline.after = c(-1,0,0,3,6,9,nrow(print_gof_stats)))
@
